---
title: "House - Rent"
output: github_document
Author : "Bhasheyam Krishnan"
---

```{r}
house_train = read.csv(file = "train.csv")
house_test = read.csv(file = "test.csv")
```

```{r}
dim(house_train)
```

From the above we can see they are many features and very small amount of instance. 

```{r}
anyNA(house_train)
anyNA(house_test)
```

Both have missing values

```{r}
sum(is.na(house_train))
sum(is.na(house_test))
```


We can see there were more missing values missing values

```{r}
train_miss = colnames(house_train)[colSums(is.na(house_train)) > 0]
```



```{r}
test_miss = colnames(house_test)[colSums(is.na(house_test)) > 0]
```

```{r}
for(name1 in train_miss){
  if(is.numeric(house_train[[name1]])){
    tempmean = mean(house_train[[name1]], na.rm = TRUE)
    house_train[[name1]][ is.na(house_train[[name1]])] = tempmean
    
  }
}
```



```{r}
for(name1 in test_miss){
  if(is.numeric(house_test[[name1]])){
    tempmean1 = mean(house_test[[name1]], na.rm  = TRUE)
    print(tempmean1)
    house_test[[name1]][ is.na(house_test[[name1]])] = tempmean1
    
  }
}
```


```{r}
sum(is.na(house_train))
sum(is.na(house_test))
```
Now deal with character features adding a level called None
```{r}
train_miss1 = colnames(house_train)[colSums(is.na(house_train)) > 0]
```



```{r}
test_miss1 = colnames(house_test)[colSums(is.na(house_test)) > 0]
```

```{r}
for(name1 in train_miss1){
  levels <- levels(house_train[[name1]])
  if ("None" %in% levels){
    
  }
  else{
    levels[length(levels) + 1] <- "None"
  }

house_train[[name1]]  = factor(house_train[[name1]],levels = levels)
house_train[[name1]][is.na(house_train[[name1]])] = "None"

    
  
}
```



```{r}
for(name1 in test_miss1){
  levels <- levels(house_test[[name1]])
if ("None" %in% levels){
    
  }
  else{
    levels[length(levels) + 1] <- "None"
  }

house_test[[name1]]  = factor(house_test[[name1]],levels = levels)
house_test[[name1]][is.na(house_test[[name1]])] = "None"
  
}
```

```{r}
sum(is.na(house_train))
sum(is.na(house_test))
```


lets clear the year feature
```{r}
house_train$GarageYrBlt = as.integer(house_train$GarageYrBlt)
house_test$GarageYrBlt = as.integer(house_test$GarageYrBlt)
```

Now lets make the features with level to factors

before that lets remove the features like name, id, street address like common facotrs


```{r}
summary(house_train)
```



```{r}
fix(house_train)
```


```{r}
library(ggplot2)
ggplot(house_train, aes(x =OverallQual, y = SalePrice)) + geom_point(color = "green") + theme_dark()

```


```{r}
library(ggplot2)
ggplot(house_train, aes(x =OverallCond, y = SalePrice)) + geom_point(color = "green") + theme_dark()
```


we can see a un usual price hike in overall condition .average rate seems to have more price.



```{r}
library(ggplot2)
ggplot(house_train, aes(x =YearBuilt, y = SalePrice)) + geom_point(color = "green") + theme_dark()
```
from the year we can see the graudual increse, new house has higher rates

```{r}
library(ggplot2)
ggplot(house_train, aes(x =Neighborhood, y = SalePrice)) + geom_point(color = "green") + theme_dark() + scale_x_discrete(labels = abbreviate)
```

the neighbourhood names are not clear but it is importan to know the variation.

```{r}
library(ggplot2)
ggplot(house_train, aes(x =YearRemodAdd, y = SalePrice)) + geom_point(color = "green") + theme_dark() 
```

modified also makes no big different, same as year bulit.

HouseStyle
```{r}
library(ggplot2)
ggplot(house_train, aes(x =HouseStyle, y = SalePrice)) + geom_point(color = "green") + theme_dark() 
```

 
 
```{r}
library(ggplot2)
ggplot(house_train, aes(x =HouseStyle)) + geom_bar(aes(fill = LandContour)) + theme_dark() 
```

we can see 1 story and  2story is more prefered. and highly paid. with different land contours



```{r}
library(ggplot2)
ggplot(house_train, aes(x =LotArea, y = SalePrice)) + geom_point(color = "green") + theme_dark() 
```


We can see a linear relation between these two.


```{r}
library(ggplot2)
ggplot(house_train, aes(x =GarageArea, y = SalePrice)) + geom_point(color = "green") + theme_dark() 
```


GrageArea also have linear relation with the price.







Now we saw many features are numeric, year, and factors. so before we



```{r}
library(Boruta)
house_selection = Boruta(SalePrice ~ . , data = house_train, doTrace = 2)
```


```{r}
train_selected = getSelectedAttributes(house_selection, withTentative = F)
train_selected
```



























