---
title: "Untitled"
output: github_document
author: "Bhasheyam Krishnan"
---

Loading the dataset

```{r}

energy = read.csv(file = "energydata_complete.csv")
```

```{r}
energy[energy == " "] = NA
```

```{r}
sum(is.na(energy))
```
From the above we can found no Missing values
```{r}
summary(energy)
```

From the above we can observe that all are nuemeric values and Date features is of the type Date.

So lets Process the Date Feature.




```{r}
head(energy)
```


```{r}
energy$date <- strptime(as.character(energy$date),format="%Y-%m-%d %H:%M:%S")
energy$date <- as.POSIXct(energy$date,tz = "America/Chicago")
head(energy$date)
```

```{r}
Sys.timezone()
```

```{r}
sum(is.na(energy))
```
```{r}
energy = energy[!is.na(energy$date),]

```


```{r}
library(lubridate)
seconds = function(x){
  s <- hour(x)*3600+minute(x)*60+second(x)
  return(s)
}

energy$second = seconds(energy$date)
```


```{r}
energy$month = floor_date(energy$date,"month")
energy$hour = floor_date(energy$date,"hour")
```


```{r}
names(energy)
```



```{r}
library(plyr)

energy_data_Total_per_hour <-  ddply(energy, "month", summarise,
                                     Appliances=sum(Appliances))
```


```{r}
head(energy)
```
```{r}
energy_data_Total_per_hour
```
```{r}
library(ggplot2)
ggplot(energy_data_Total_per_hour,aes(x=month,y = Appliances)) +  geom_point(color = "green",size = 12) + theme_dark()
```
The above is the we can use the use of the appliance in the 5 months

```{r}
library(plyr)
energy_data_Total_per_hour_1 = ddply(energy,"hour", summarise,Appliances=sum(Appliances))
```

```{r}
library(ggplot2)
ggplot(energy_data_Total_per_hour_1,aes(x=hour,y = Appliances)) +  geom_point(color = "green",size = 1) + theme_dark()
```

From the above the use of applicane is almost similar for the months
on hour basis

```{r}
library(plyr)

energy_data_Total_light_per_hour <-  ddply(energy, "month", summarise,
                                     lights=sum(lights))
```



```{r}
library(ggplot2)
ggplot(energy_data_Total_light_per_hour,aes(x=month,y = lights)) +  geom_point(color = "green") + theme_dark()
```
The above is the we can use the use of the appliance in the 5 months

```{r}
library(plyr)
energy_data_Total_per_hour_light = ddply(energy,"hour", summarise, lights=sum(lights))
```
```{r}
library(ggplot2)
ggplot(energy_data_Total_per_hour_light,aes(x=hour,y = lights)) +  geom_point(color = "green",size = 1) + theme_dark()
```

From the above we can observe the use of the lights is hight initially and decresed in later months


since we have more features lets first try to reduce the number of features




```{r}
str(energy)
dim(energy)
names(energy)
```


```{r}
library(caret)
energy.lm.fit = train(Appliances~., data=energy[,c(2:29)],  method="lm",
                 metric='RMSE')
```

```{r}
summary(energy.lm.fit)
```
From the above we can see few of the features are not statitically significant we can observe from the P - Values

And the Square error is very low which show the poor fit of the model 


```{r}
resudals = resid(energy.lm.fit)
energy_result = as.data.frame(resudals)
energy_result$actual = energy$Appliances
energy_result$predicted = predict(energy.lm.fit)
```
```{r}
plot(energy[2:10])
```

```{r}
barplot(energy_result$resudals)
```

The Residuals is not even and distributed randomly . so the model fit is very poor
```{r}
library(ggplot2)
ggplot(energy_result,aes(x=actual,y=predicted))+geom_point(color = "green") + theme_dark()
```

